Moral Foundations of U.S. Political News Organizations

### 2019-04-07 pilot_manuscript.Rmd
FIXED IT

```{r data_clean_kav, eval = T, echo = F}
##combine all kav data into one dataset
#read it in
NYtimes_kav = read.csv("exp2_data/NYtimes_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok
NPR_kav = read.csv("exp2_data/NPR_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok
SLATE_kav = read.csv("exp2_data/SLATE_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok
HUFFPO_kav = read.csv("exp2_data/HUFFPO_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #not ok fix
POLITICO_kav = read.csv("exp2_data/POLITICO_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok 
FOX_kav = read.csv("exp2_data/FOX_kav.csv", stringsAsFactors = F) #ok 
BREITBART_kav = read.csv("exp2_data/BREITBART_kav.csv", stringsAsFactors = F) #ok
RUSH_kav = read.csv("exp2_data/RUSH_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok 
BLAZE_kav = read.csv("exp2_data/BLAZE_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok 
HANNITY_kav = read.csv("exp2_data/HANNITY_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok

@@

@@

```{r data_clean_gs, eval = T, echo = F}
##combine all gs data into one dataset
#read it in
NYtimes_gs = read.csv("exp2_data/NYtimes_gs.csv", stringsAsFactors = F, fileEncoding = "UTF-8") #not ok 
NPR_gs = read.csv("exp2_data/NPR_gs.csv", stringsAsFactors = F) #ok
SLATE_gs = read.csv("exp2_data/SLATE_gs.csv", stringsAsFactors = F) #ok 
HUFFPO_gs = read.csv("exp2_data/HUFFPO_gs.csv", stringsAsFactors = F) #ok 
POLITICO_gs = read.csv("exp2_data/POLITICO_gs.csv", stringsAsFactors = F, fileEncoding = "UTF-8") #not ok 
FOX_gs = read.csv("exp2_data/FOX_gs.csv", stringsAsFactors = F) #ok 
BREITBART_gs = read.csv("exp2_data/BREITBART_gs.csv", stringsAsFactors = F) #ok 
RUSH_gs = read.csv("exp2_data/RUSH_gs.csv", stringsAsFactors = F, fileEncoding = "UTF-8") #not ok 
BLAZE_gs = read.csv("exp2_data/BLAZE_gs.csv", stringsAsFactors = F) #ok 
HANNITY_gs = read.csv("exp2_data/HANNITY_gs.csv", stringsAsFactors = F) #ok

@@

@@

## Results
```{r exp2 source descriptives_both, results = 'asis', echo = FALSE, message = F}
#Kav
final_kav$uniquewords = NA
final_kav$valenceavg = NA

>>>>

```{r data_clean_kav, eval = T, echo = F}
##combine all kav data into one dataset
#read it in
NYtimes_kav = read.csv("exp2_data/NYtimes_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok
NPR_kav = read.csv("exp2_data/NPR_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok
SLATE_kav = read.csv("exp2_data/SLATE_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok
HUFFPO_kav = read.csv("exp2_data/HUFFPO_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok
POLITICO_kav = read.csv("exp2_data/POLITICO_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok 
FOX_kav = read.csv("exp2_data/FOX_kav.csv", stringsAsFactors = F) #ok 
BREITBART_kav = read.csv("exp2_data/BREITBART_kav.csv", stringsAsFactors = F) #ok
RUSH_kav = read.csv("exp2_data/RUSH_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok 
BLAZE_kav = read.csv("exp2_data/BLAZE_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok 
HANNITY_kav = read.csv("exp2_data/HANNITY_kav.csv", stringsAsFactors = F, fileEncoding="UTF-8") #ok

@@

#fix this issue
master_kav$Text = gsub("\\.", "\\. ", master_kav$Text)

@@

```{r data_clean_gs, eval = T, echo = F}
##combine all gs data into one dataset
#read it in
NYtimes_gs = read.csv("exp2_data/NYtimes_gs.csv", stringsAsFactors = F, fileEncoding = "UTF-8") #ok
NPR_gs = read.csv("exp2_data/NPR_gs.csv", stringsAsFactors = F) #ok
SLATE_gs = read.csv("exp2_data/SLATE_gs.csv", stringsAsFactors = F) #ok 
HUFFPO_gs = read.csv("exp2_data/HUFFPO_gs.csv", stringsAsFactors = F) #ok 
POLITICO_gs = read.csv("exp2_data/POLITICO_gs.csv", stringsAsFactors = F, fileEncoding = "UTF-8") #not ok 
FOX_gs = read.csv("exp2_data/FOX_gs.csv", stringsAsFactors = F) #ok 
BREITBART_gs = read.csv("exp2_data/BREITBART_gs.csv", stringsAsFactors = F) #ok 
RUSH_gs = read.csv("exp2_data/RUSH_gs.csv", stringsAsFactors = F, fileEncoding = "UTF-8") #not ok 
BLAZE_gs = read.csv("exp2_data/BLAZE_gs.csv", stringsAsFactors = F) #ok 
HANNITY_gs = read.csv("exp2_data/HANNITY_gs.csv", stringsAsFactors = F) #ok

@@

#fix this issue
master_gs$Text = gsub("\\.", "\\. ", master_gs$Text)

@@

## Results

```{r exp2 source descriptives_both, results = 'asis', echo = FALSE, message = F}
#Kav
final_kav$uniquewords = NA
final_kav$valenceavg = NA
